Report for Qualifying Exam

### 2024-07-22 src/sections/relatedwork.tex
modified the table, added citations

\begin{table}[]
\centering
\small
\begin{tabular}{@{}llllll@{}}
\toprule
\multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Linguistic \\ Change\end{tabular}}} & \multicolumn{1}{c}{\textbf{Approach}}                                              & \multicolumn{1}{c}{\textbf{TCD}} & \multicolumn{3}{c}{\textbf{Example}}                                                                                                                                                                 \\ \cmidrule(l){4-6}
\multicolumn{1}{c}{\textbf{}}                                                             & \multicolumn{1}{c}{\textbf{}}                                              & \multicolumn{1}{c}{\textbf{}}    & \textbf{Word}         & \textbf{Former Usage}                                                                & \textbf{New Usage}                                                                    \\ \midrule
\multicolumn{1}{l}{\textbf{Semantic}}                                                     & \multicolumn{1}{l}{\textbf{FREQUENCY}}                                             & \multicolumn{1}{l}{}            & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}                                                                & \multicolumn{1}{l}{}                                                                 \\ \midrule
\textbf{}                                                                                 & Log Ratio                                                                  & 1960 \& 1990                     & disk                  & -                                                                                    & -                                                                                     \\ \cmidrule(l){2-6}
\textbf{}                                                                                 & \begin{tabular}[c]{@{}l@{}}Word \\ Frequency\end{tabular}                  & 1900--2005                      & bitch                 & female dog                                                                           & slang                                                                                 \\ \cmidrule(l){2-6}
\textbf{}                                                                                 & \begin{tabular}[c]{@{}l@{}}Law of \\ Conformity\end{tabular}               & 1800--2000                      & -                     & -                                                                                    & -                                                                                     \\ \cmidrule(l){2-6}
                                                                                          & \textbf{DISTRIBUTIONAL}                                                             &                                  &                       &                                                                                      &                                                                              \\ \cmidrule(l){2-6}

@@

                                                                                          & \textbf{PART OF SPEECH}                                                                        &                                  &                       &                                                                                      &                                                                   \\ \midrule

>>>>

\begin{table}[]
\centering
\small
\begin{tabular}{@{}llllll@{}}
\toprule
\multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Linguistic \\ Change\end{tabular}}} & \multicolumn{1}{c}{\textbf{Approach}}                                              & \multicolumn{1}{c}{\textbf{TCD}} & \multicolumn{3}{c}{\textbf{Example}}                                                                                                                                                                 \\ \cmidrule(l){4-6}
\multicolumn{1}{c}{\textbf{}}                                                             & \multicolumn{1}{c}{\textbf{}}                                              & \multicolumn{1}{c}{\textbf{}}    & \textbf{Word}         & \textbf{Former Usage}                                                                & \textbf{New Usage}                                                                    \\ \midrule
\multicolumn{1}{l}{\textbf{Semantic}}                                                     & \multicolumn{5}{c}{\textbf{FREQUENCY \cite{gulordava-baroni-2011-distributional, kulkarni2014statisticallysignificantdetectionlinguistic, hamilton-etal-2016-diachronic}}}                                             &            &  &                                                                &                                                                 \\ \midrule
\textbf{}                                                                                 & Log Ratio                                                                  & 1960 \& 1990                     & disk                  & -                                                                                    & -                                                                                     \\ \cmidrule(l){2-6}
\textbf{}                                                                                 & \begin{tabular}[c]{@{}l@{}}Word \\ Frequency\end{tabular}                  & 1900--2005                      & bitch                 & female dog                                                                           & slang                                                                                 \\ \cmidrule(l){2-6}

                                                                                          & \multicolumn{5}{c}{\textbf{DISTRIBUTIONAL \cite{gulordava-baroni-2011-distributional, kim-etal-2014-temporal, kulkarni2014statisticallysignificantdetectionlinguistic, 10.1007/978-3-319-50496-4_18, hamilton-etal-2016-diachronic, hamilton-etal-2016-cultural, 10.1162/opmi_a_00081, giulianelli-etal-2020-analysing}}}                                                              &                                  &                       &                                                                                      &                                                                              \\ \cmidrule(l){2-6}

@@

                                                                                          & \multicolumn{5}{c}{\textbf{PART OF SPEECH \cite{kulkarni2014statisticallysignificantdetectionlinguistic, hamilton-etal-2016-cultural}}}                                                                       &                                  &                       &                                                                                      &                                                                   \\ \midrule
